literature coding explore

### 2024-02-03 docs/lit_codes_explore.qmd
update lit coding explore

---
title: "literature coding explore"
date: "`r Sys.Date()`"
format:
 html: 
  self-contained: true
editor: visual
toc: TRUE
toc-title: "On this page"
theme: yeti
fontcolor: "#134f5c"
---

>>>>

---
title: "literature coding explore"
author: "Emily Nazario | UC Santa Cruz | enazario'@'ucsc.edu"
date: "`r Sys.Date()`"
format:
 html: 
  self-contained: true
editor: visual
toc: TRUE
toc-title: "On this page"
theme: yeti
fontcolor: "#134f5c"
---
